---
title: "DMP Tools Actionable"
author: "Gerald Weber, Helmuth Breitenfellner"
date: "01.07.2019"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Make DMP Tools Actionable

* **194.045 Data Stewardship 2019S**
* Gerald Weber, 0125536
* Helmuth Breitenfellner, 08725866

# Link to GitHub Pages

[https://helmuthb.github.io/dmp-tools-actionable/](https://helmuthb.github.io/dmp-tools-actionable/)

# Set Up Instance of RDMO

We have been setting up an instance of RDMO on a virtualized environment, using Docker.
The installation can be used at [rdmo.helmuth.at](https://rdmo.helmuth.at).

For this part of the exercise we have been using the docker-compose version of RDMO
as available on [GitHub](https://github.com/rdmorganiser/rdmo-docker-compose).

## Re-created DMP in RDMO

# RDA DMP Export for RDMO

## Approach to Connect with RDMO

We were investigating the following possible ways of connecting with an RDMO instance:

* Database connection
* RDMO API
* XML export from RDMO

Using the database access was considered the last resort, as this would be dependend
on internal data structures of the tool.

The RDMO API did originally sound very promising. However, we found that existing
installations often disabled the API
(e.g. [rdmo-demo.uibk.ac.at/](http://rdmo-demo.uibk.ac.at/)),
or the API is not accessible for regular users.

We settled on the third option, which is using the XML which can be exported from a
project in the RDMO user interface.
This allows using the export tool for regular users, even if the API has been
disabled in the installation.

## Using the Tool

The tool is now a simple command line tool.
As a precondition, the user has to export the project as XML from RDMO.
Then the tool can be started with
```
python3 xml2madmp.py <rdmo-export.xml> <ma-dmp.json>
```

## License

The tool is licensed under the [MIT license](https://opensource.org/licenses/MIT).

# Mapping existing DMP templates to RDA DMP Common Standard

For this part of the exercise we have used a two-part mapping.

First, we created a questionaire based on the Horizon 2020 template and FWF template, which maps the
questions to the corresponding fields and attributes of the RDMO model.

Then, we were applying our mapping from RDMO attributes to the [RDA DMP Common Standard](https://github.com/RDA-DMP-Common/RDA-DMP-Common-Standard).

## Map Horizon 2020 template to RDA DMP Common Standard

Some of the questions from Horizon 2020 do not clearly map to attributes in the RDMO data model.
We were using guidelines from the existing Horizon 2020 view which performs the mapping into the other direction.

### Fermont Bridge DMP

* [Horizon 2020 PDF version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/h2020-gerald.pdf)
* [RDA DMP Common Standard JSON version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/h2020-gerald.json)

### Salzburg - US Wheat DMP

* [Horizon 2020 PDF version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/h2020-helmuth.pdf)
* [RDA DMP Common Standard JSON version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/h2020-helmuth.json)

## Map FWF template to RDA DMP Common Standard

Similar issues as in the case of Horizon 2020 were encountered.
In addition, we did not cater for the last case when no data is processed, as a DMP is then not needed at all.

### Fermont Bridge DMP

* [FWF PDF version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/fwf-gerald.pdf)
* [RDA DMP Common Standard JSON version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/fwf-gerald.json)

### Salzburg - US Wheat DMP

* [FWF PDF version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/fwf-helmuth.pdf)
* [RDA DMP Common Standard JSON version](https://github.com/helmuthb/dmp-tools-actionable/blob/master/DMP%20Samples/fwf-helmuth.json)

```{r child = 'docs/field_mapping.md'}
```